A thesis draft

### 2018-10-03 draft.tex
Add section on tcp split

TUN/TAP and IP over IP maintain the connection transparency incapsulating the 
packet in another one. In this way, the original packet remains preserved and it 
becomes the new packet payload\todo{Make an image showing a packet inside 
another packet, to make easy to understand what we're meaning here}, that can 
be elaborated and modified accordingly, until it gets decapsulated and sent to 
$R$ eventually. When $R$ receives the packet, it is not be aware of the packet 
elaboration, since all the original headers were preserved (or slightly 
modified). TCP session recreation, instead, ``split'' the TCP session in two 
endpoints: an Ingress, that manage the connection with the client and an 
Egress, that communicate with the packet receiver. In order to achieve that, a 
session table needs to be established and continuously updated, while TCP 
headers need to be accordingly modified to allow data transmission through the 
Ingress and Egress points. TCP session recreation seems burdersome at the first 
sight, but it offers the flexibility to perform extensive packet manipulation: 
since the packet its recreated every time at the Ingress and Egress points, 
while in the Network Function Virtualization Infrastructure (NFVI), the 
original packet can be stripped of its headers (that could be saved in the 
session table) to slightly improve internal packet transmission. \todo{Insert 
TCP session recreation schema}

During the testbed development we first tried the TUN/TAP solution, that 
revealed to be not completely transparent and with major performance drawbacks 
(i.e. packet transmission in a LAN connection reached latencies of 50ms) 
\todo{Explain the constraint of point-to-point connections, while we need 
dynamic SFC)}

>>>>

TUN/TAP and IP over IP maintain the connection transparency incapsulating the 
packet in another one. In this way, the original packet remains preserved and it 
becomes the new packet payload\todo{Make an image showing a packet inside 
another packet, to make easy to understand what we're meaning here}, that can 
be elaborated and modified accordingly, until it gets decapsulated and sent to 
$R$ eventually. When $R$ receives the packet, it is not be aware of the packet 
elaboration, since all the original headers were preserved (or slightly 
modified).
